Effect of character correlation

### 2017-09-19 Analysis/EffectCorrelationStats.Rmd
Stats updated

Effect of character correlation
===============

Loading the functions and the data
-----------------------------------

@@

Pooled results
=================

Effect of character correlation per scenario
-----------------

@@

Effect of character correlation per number of character
-----------------

Effect of character correlation per number of taxa
-----------------

Effect of character correlation per methods
-----------------

Individual results
=================

@@

Summary statistics
-----------------

@@

Nested anova
-----------------------------------

@@

Distributions probability overlap (Bhattacharrya Coefficient)
-----------------------------------

@@

Non-parametric pairwise comparisons
-----------------------------------

>>>>

# Effect of character correlation

## Loading the functions and the data

@@

# Pooled results

## Effect of character correlation per scenario

@@

## Effect of character correlation per number of character

```{r, warning = FALSE}
## Pooling the data per character
character_RF_norm <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "RF", best = "norm")
character_Tr_norm <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "Tr", best = "norm")
character_RF_null <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "RF", best = "rand")
character_Tr_null <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "Tr", best = "rand")

## Combining the data into a table
characters <- pool.table(list(character_RF_norm, character_Tr_norm, character_RF_null, character_Tr_null),
                    comp.label = comp.labels, metric.label = metric.labels, label.param = "character")
```

```{r, echo = FALSE}
## Setting the table captions
captions_pooled_characters <- paste("Summary statistics of the normalised distances to the best or null tree for the pooled number of characters.")

## Printing the tables
kable(characters, row.names = FALSE, caption = captions_pooled_characters)
```

```{r, eval = FALSE, echo = FALSE}
make.xtable(characters, caption = captions_pooled_characters, label = "Tab_pooledcharacters")
```

### Testing the effect of the number of characters on the NTS

```{r}
## Applying an lm to all the data
results <- test.effect.aov(whole_data, formula = NTS ~ character, fun = lm)
```

```{r, warning = FALSE}
## Summarise into a table
character_list <- list(character_RF_norm, character_Tr_norm, character_RF_null, character_Tr_null)
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)
test_table <- pair.test.table(character_list, comp.label = comp.labels, metric.label = metric.labels)
```

```{r, echo = FALSE}
## Caption
cap_pool_char_test <- paste("Difference between the pooled number of characters. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

## Printing the tables
kable(test_table, row.names = FALSE, caption = cap_pool_char_test)
```

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_char_test, label = "Tab_pooledscharacters_test")
```

## Effect of character correlation per number of taxa

```{r, warning = FALSE}
## Pooling the data per taxa
taxa_RF_norm <- multi.pool(whole_data, param = c("t25", "t75", "t150"),
                               metric = "RF", best = "norm")
taxa_Tr_norm <- multi.pool(whole_data, param = c("t25", "t75", "t150"),
                               metric = "Tr", best = "norm")
taxa_RF_null <- multi.pool(whole_data, param = c("t25", "t75", "t150"),
                               metric = "RF", best = "rand")
taxa_Tr_null <- multi.pool(whole_data, param = c("t25", "t75", "t150"),
                               metric = "Tr", best = "rand")

## Combining the data into a table
taxa <- pool.table(list(taxa_RF_norm, taxa_Tr_norm, taxa_RF_null, taxa_Tr_null),
                    comp.label = comp.labels, metric.label = metric.labels, label.param = "taxa")
```

```{r, echo = FALSE}
## Setting the table captions
captions_pooled_taxa <- paste("Summary statistics of the normalised distances to the best or null tree for the pooled number of taxa.")

## Printing the tables
kable(taxa, row.names = FALSE, caption = captions_pooled_taxa)
```

```{r, eval = FALSE, echo = FALSE}
make.xtable(taxas, caption = captions_pooled_taxas, label = "Tab_pooledtaxa")
```

### Testing the effect of the method on the NTS

```{r}
## Applying an lm to all the data
results <- test.effect.aov(whole_data, formula = NTS ~ taxa, fun = lm)
```

```{r, warning = FALSE}
## Summarise into a table
taxa_list <- list(taxa_RF_norm, taxa_Tr_norm, taxa_RF_null, taxa_Tr_null)
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)
test_table <- pair.test.table(taxa_list, comp.label = comp.labels, metric.label = metric.labels)
```

```{r, echo = FALSE}
## Caption
cap_pool_tax_test <- paste("Difference between the pooled number of taxa. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

## Printing the tables
kable(test_table, row.names = FALSE, caption = cap_pool_tax_test)
```

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_tax_test, label = "Tab_pooledstaxa_test")
```

## Effect of character correlation per methods

```{r, warning = FALSE}
## Pooling the data per taxa
method_RF_norm <- multi.pool(whole_data, param = c("bayesian", "parsimony"),
                               metric = "RF", best = "norm")
method_Tr_norm <- multi.pool(whole_data, param =c("bayesian", "parsimony"),
                               metric = "Tr", best = "norm")
method_RF_null <- multi.pool(whole_data, param = c("bayesian", "parsimony"),
                               metric = "RF", best = "rand")
method_Tr_null <- multi.pool(whole_data, param = c("bayesian", "parsimony"),
                               metric = "Tr", best = "rand")

## Preparing the table labels
comp.labels <- c("Best", rep("", 3), "Null", rep("", 3))
metric.labels <- rep(c("RF", "", "Tr", ""), 2)

## Combining the data into a table
methods <- pool.table(list(method_RF_norm, method_Tr_norm, method_RF_null, method_Tr_null),
                    comp.label = comp.labels, metric.label = metric.labels, label.param = "method")
```

```{r, echo = FALSE}
## Setting the table captions
captions_pooled_methods <- paste("Summary statistics of the normalised distances to the best or null tree for the pooled methods.")

## Printing the tables
kable(methods, row.names = FALSE, caption = captions_pooled_methods)
```

```{r, eval = FALSE, echo = FALSE}
make.xtable(methods, caption = captions_pooled_methods, label = "Tab_pooledmethod")
```

### Testing the effect of the method on the NTS

```{r}
## Applying an lm to all the data
results <- test.effect.aov(whole_data, formula = NTS ~ method, fun = lm)
```

```{r, warning = FALSE}
## Summarise into a table
methods_list <- list(method_RF_norm, method_Tr_norm, method_RF_null, method_Tr_null)
comp.labels <- c("Best", rep("", 3), "Null", rep("", 3))
metric.labels <- rep(c("RF", "", "Tr", ""), 2)
test_table <- pair.test.table(methods_list, comp.label = comp.labels, metric.label = metric.labels)
```

```{r, echo = FALSE}
## Caption
cap_pool_met_test <- paste("Difference between the pooled methods. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

## Printing the tables
kable(test_table, row.names = FALSE, caption = cap_pool_met_test)
```

```{r, eval = FALSE, echo = FALSE}
make.xtable(test_table, caption = cap_pool_met_test, label = "Tab_pooledsmethods_test")
```

# Individual results

@@

## Summary statistics

@@

## Nested anova

@@

## Distributions probability overlap (Bhattacharrya Coefficient)

@@

## Non-parametric pairwise comparisons
